## Data check
```{r}
data <- read.csv("data/data_student.csv")
summary(data)
```
## Tidyverse library
```{r}
library(tidyverse)
```

# Descriptive Statistics
```{r}
data %>% # "tibble" = table of data
  summarise_if(is.numeric, list( #Apply summary functions only if the column is numeric
    mean = mean,
    sd = sd,
    median = median,
    quantile = quantile,
    min = min,
    max = max
  ), na.rm = TRUE) # Ignore missing values
summary(data)
```
# Explain why the summary is different from one column to the next.
> Because on one hand there are text columns (like Name/First Name/City...) and on the other hand, there are "numeric" ones (Weight, Height, YearsIn...). It depends on the column type.

## Weight histogram
```{r}
hist(data$Weight, 
     main = "Weight Histogram", 
     xlab = "Weight",
     col = "orange", 
     border = "black")
```
# Weight densitogram
```{r}
plot(density(data$Weight, na.rm = TRUE),
     main = "Weight Densitogram",
     xlab = "Weight",
     ylab = "Density",
     col = "orange",
     lwd = 2)
```
## Weight Boxplot
```{r}
# Boxplot for the 'Weight' column
boxplot(data$Weight,
        main = "Weight Boxplot",
        ylab = "Weight",
        col = "orange")
```
## Boxplot section
# Reference URL > https://www.geeksforgeeks.org/machine-learning/box-plot/
What are the main elements of a boxplot?
* Minimum - It is the minimum value in the dataset excluding the outliers.
* First Quartile (Q1) - 25% of the data lies below the First (lower) Quartile.
* Median (Q2) - It is the mid-point of the dataset. Half of the values lie below it and half above.
* Third Quartile (Q3) - 75% of the data lies below the Third (Upper) Quartile.
* Maximum - It is the maximum value in the dataset excluding the outliers.

Why is a boxplot the starting point of choice in summarizing an unknown distribution?
* Box plots provide a visual summary of the data with which we can quickly identify the average value of the data, how dispersed the data is, whether the data is skewed or not (skewness).

## Histogram of Weight by Gender
```{r}
hist(data$Weight[data$Gender == "F"], #Condition F
     col = "pink",
     xlim = range(data$Weight, na.rm = TRUE), 
     main = "Histogram of Weight by Gender",
     xlab = "Weight",
     ylab = "Frequence",
     ylim = c(0, 2))

hist(data$Weight[data$Gender == "M"], #Condition M
     col = "blue",
     add = TRUE)

legend("topright", legend = c("F", "M"),
       fill = c("pink", "blue"))
hist(data$Weight, ylim = c(0, 50))
```

## Boxplot of Weight by Gender
```{r}
boxplot(Weight ~ Gender, data = data,
        main = "Weight Distribution by Gender",
        xlab = "Gender",
        ylab = "Weight",
        col = c("pink", "lightblue"),
        ylim = c(45,85))
```
#Better visualization of the dispersion...

## Significant Difference or not ?

#What statistical test is best to answer this question?
Co pilot anwser :
* A t-test (specifically, an independent samples t-test) is appropriate to compare the mean weights between two groups (men vs. women). If the data are not normally distributed, use a Wilcoxon rank-sum test.

```{r}
wilcox.test(Weight ~ Gender, data = data)
```
# > No significant
Since the effect size is large, it suggests that with a larger sample, the difference would likely become statistically significant
